Accessible, realistic genome simulation with selection using \stdpopsim

### 2025-07-25 review-responses.tex

  Thanks -- we're glad you appreciate both the project and the paper.

  \begin{point}{}
    Perhaps my main constructive reaction is that this paper is a bit light on information about the ways in which the new selection features are implemented. 
    There is a section "implementing selection in stdpopsim", but it is not always easy to figure out from the description here how things work under the hood. 
    Instead, the section is more like a short tour of the new features aimed at users. 
    Moreover, there is no section of the methods that really goes over the details of implementation. 
    The ms says that SLiM is the backend, but there aren't many details about how information passed into stdpopsim is translated into SLiM. 
    It's also not clear to me how the selective sweep mode is implemented, given that it gives users the option to condition on some range of starting and ending allele frequencies. 
    I assume that the approach is to run full SLiM iterations until the sweep ends up as desired (though it may not be)? 
    But one might also simulate the allele-frequency trajectory for the sweeping allele alone until one "works", 
    and then do coalescent simulations to fill in flanking variation conditional on the allele-frequency trajectory, 
    a la Hudson \& Kaplan '88 (though I don't quite see how one would do this simultaneously with background selection, 
    which the sweep simulations include). In any case, I'm not sure how the conditions are being achieved from reading the paper. 
    (I've refrained from looking at the online documentation for stdpopsim 0.3.0, where there may be more answers, in order to review the paper as an independent product.) 
    I don't think the paper necessarily needs loads more text on this, but I think there should be more information hinting at implementation in main text and probably a new methods subsection with further details.  
\end{point}

  \reply{
     %IG: I added this because the section I added for comment 1.5 below seems relevant here as well.
     %    I think that this addresses the first part of the rev's comment, but details need to also be added for selective sweeps
     We added a new section to the methods that provides detials on how DFE models are implemented using DFE objects \revref.
     The end of this section contains a brief description of how the simulation engine uses the information specified in a given DFE object when sampling a new mutation,
     and how the conditioning for selective sweeps is implemented
     (indeed, by rejection sampling).
     We've also added a small note earlier in the paper, at \llname{sweep_conditioning}.
  }

@@

  \begin{point}{\revref} 
    Relatedly, why is the dominance coefficient currently limited to between 0 and 1? It's fine that it is for now, but I was curious what makes it more difficult to include other values of h.
  \end{point}

  \reply{
      This was a mistake in the original submission. The dominance coefficient is not limited to values between 0 and 1, and the 
      implementation allows for overdominance and underdominance. This clause has been removed \revref,
      %IG: I added a note about this in the 2nd part of the newly added methods section
      and in the newly added methods section about DFE models, we added an explicit note that dominance coefficients can be negative or larger than 1. 
  }

  \begin{point}{} 
    I think it would be helpful to say a bit more about the vaquita earlier in the manuscript. Although some of the authors have worked on the vaquita recently, it is still a fairly obscure organism, 
    so it would be worth describing its unfortunate situation and why it is an interesting comparison with humans throughout these simulations.  
\end{point}

  \reply{
      Good idea; we have added a bit more context, at \revref and \llname{vaquita_note}.
  }

@@

  \begin{point}{} % 
    It seems as though everything on the backend is being done by SLiM in the demonstrations here 
    (unless I'm missing something about how the sweeps are done), so the runtimes are not really the product of the effort of the authors here. 
    Still, I think it would be good to provide a bit more information on the runtimes for prospective users to get a sense of what doing selection in stdpopsim entails. 
    (It's mentioned that the sweeps were time-consuming, but details aren't given as far as I can tell.)  
\end{point}

  \reply{
      TODO. 
  }

  \begin{point}{}
    Point of clarification about the flexibility of DFE specification: Is the DFE allowed to be a mixture distribution in a single genomic region? 
    Generally, the paper mentions users can provide a custom DFE, but what does that mean in practice? Does it have to be of a particular distribution family or form? 
    (i.e. the paper mentions "fixed value, normally-distributed, gamma-distributed"). 
    The vaquita DFE seems to be a mixture of several nonoverlapping DFEs with different h values, which suggests to me substantial flexibility, 
    but I'm not quite clear on the limits. Most of the figures feature fairly few replicates, which makes me think that these simulations are necessarily time/compute intensive.
  \end{point}

@@

  \reply{
     We added a section to the methods with more details on \stdpopsim's DFE class, which answers these questions \revref.
     In particular, we clarified that each DFE model is a mixture of different mutation types,
     and we specified the distribution families that are currently supported by \stdpopsim.
     We also described in greater detail how the relationship between dominance and selection coefficients is implemented,
     which as the reviewer guessed, is done separately for each mutation type in the mixture.
     This framework was designed to be very flexible, while allowing the implementation of most DFE models with few lines of code.
  }

  \begin{point}{\revref}
      Sentence starting [here] % on line 383 
      about difficulty identifying $h$ and $s$ separately seems to be missing some important citations, 
      e.g. \textcite{fuller2019measuring}, % Fuller et al 2019 (pmid 30962618) and citations therein, 
      including 
      \textcite{simons2014deleterious}; % Simons et al 2014;
      \textcite{wright1937distribution}. % Wright 1937.
  \end{point}

  \reply{
      Good point; done \revref; note that we didn't make the list of citations as long as we might have,
      opting instead to direct readers to \textcite{fuller2019measuring} for the review.
  }

  \begin{point}{}
    It might bear further comment that the gamma distribution is not flexible enough to accommodate the distribution of hs in the vaquita simulation 
    (which is what the DFE inference methods can really see), even if the s values are gamma distributed (bc of the big jump caused in hs by the switch in dominance). 
    This is interesting given how often gammas are used in DFE inference. The paper does mention that using h=1/2 as an assumption can lead to bad estimation of s, 
    but the point that a relationship between s and h can cause hs to be non-gamma even when s is gamma is perhaps a little more subtle. 
    Generally, I thought the lessons learned from the DFE exercise here could be put more clearly.
  \end{point}

  \reply{
    Following this insightful comment, we added a few sentences to the discussion addressing this issue, at \revref.
    % No need to provide the quote here as they can easily see the change directly using the link.
  }

  \begin{point}{}
    Related to the previous point, I found it a bit odd to that both the style of the DFE (and in particular the h/s relationship) 
    and the demography switched when comparing vaquita and human DFE. 
    It seemed like a missed opportunity to do something hinted at earlier in the manuscript: 
    namely, to try pairing demographies and DFEs from different species. 
    I.e. it would be interesting in this context to look at simulations that have the human demography and vaquita DFE and vice versa, 
    even if only in a supplementary figure.
  \end{point}

  \reply{
    Thank you for the suggestion. 
    While it is possible to mix demographies and DFEs in stdpopsim catalog and study the effects, 
    this is outside of the motivation for this paper.
    Varying both DFE and demography in a systematic way and studying the effects would be interesting and useful, 
    but there is less to learn from only swapping the DFE and demography of two species in this context.
    We have clarified the point in the manuscript that when a given species of interest does not have published demographic and DFE inferences, 
    one can be borrowed from another species as a next best option at \revref,
    and added another note about the aims of the paper, at \llname{not_the_point}.
  }

\begin{point}{\revref}
    Figure S1, right panel. Is pi being computed from all the genomes (CEU/CHB/YRI)? 
    I think it's okay given the point that's being made, 
    but it might strike some readers as odd given how much is often made of the pi differences 
    in these groups under the estimated demography, so maybe it should be said explicitly what's being done.
  \end{point}

@@

  \begin{point}{\revref} % \&75
    How do you deal with overlapping annotations in a gff?
  \end{point}

  \reply{
    TODO. \revref
  }

  \begin{point}{}
    The inference of the deleterious DFE with GRAPES is quite inaccurate. 
    Is it possible that there is a factor of 2 error involved?
  \end{point}

  \reply{
As noted in the paper, conversion of selection inferences between tools is challenging.
We thus spent quite a bit of time on this exact point,
and consulted with the developers of \polydfe and \grapes to confirm our conversions.
(The developer of \dadicli is an author on this paper.)
The inaccuracy of \grapes is a surprise to us.
Note that \grapes is also less accurate than \polydfe and \dadicli in inferring the shape of the distribution (Fig.~\ref{fig:homsap-dfe.ooa}B), which suggests the inaccuracy is not simply a scaling issue.
  }

@@

  \begin{point}{\revref} % 24:
    You cite only Gillespie 1991 on line 56. 
    Requires many more citations, with at least one to Kimura.  
\end{point}

  \reply{
  We have elaborated the list of citations for this point and have now cited Kimura as well. \revref
  }

  \begin{point}{} % 27:
    What fraction of the genome is under selection in the human genome you simulated?
  \end{point}

  \reply{
 For simulations with selection we assumed that selected mutations could only fall within exonic regions,
 thus approximately 2.1\% of the genome is under selection in human simulations and 2.2\% in vaquita simulations.
 We've added notes to this effect, at \revref{} and \llname{vaquita_percent}.
  }

  \begin{point}{\revref} % 47:
    ``This is somewhat surprising given that background selection is expected to somewhat interfere with the sweep signature.'' % (line 349-350)
      $\to$ I'm not sure what this means. 
    It's unclear to me why background selection will interfere with a sweep signature. 
    Do you have a citation for this?  
\end{point}

### 2025-07-25 analysis2_manuscript.tex

% add commands for the DFE inference methods
\newcommand{\dfe}{\texttt{dfe-alpha}\xspace}
\newcommand{\polydfe}{\texttt{polyDFE}\xspace}
\newcommand{\dadicli}{\texttt{dadi-cli}\xspace}
\newcommand{\grapes}{\texttt{GRAPES}\xspace}

@@

\section*{Introduction}
    \label{introduction}
    % selection
    Selection is a fundamental force in evolution, shaping the
    genetic diversity of populations and driving the adaptation of
    species to their environments. The effects of selection
    on genetic variation are complex, and can be difficult to disentangle
    from other evolutionary processes such as mutation, recombination,
    and genetic drift \citep[e.g.,][]{ohta1973slightly,lewontin1973distribution, kimura1985neutral, tajima1989statistical,gillespie1991causes, kern2018neutral}. \revpoint{2}{4}
    For instance, changes in population size can lead to fluctuations
    in genetic diversity across a recombining chromosome
    that can mimic the effects of selection \citep{simonsen1995properties},
    leading to spurious inferences about the strength and targets of genetic adaptation
    \citep{simonsen1995properties,akey2004population,nielsen2005genomic}.
    In turn, selection can confound our ability to infer demographic
    history from allele frequencies \citep{ewing2016consequences,schrider2016effects} and
    estimates of inverse coalescent rate \citep{schrider2016effects, johri2021impact, cousins2024accurate}.
    Thus, it is imperative to jointly account for the effects of selection
    and demography when inferring evolutionary history from genetic data \citep[e.g.,][]{sheehan2016deep,johri2020toward},
    yet the number of tools for doing so remain limited.

@@

    % goals
    Here, we provide an overview of a major new addition
    to \stdpopsim---the inclusion of models of selection.
    We begin by describing the models of selection that we have implemented,
    as well as the parameter choices that are available to the user.
    This includes models of background selection, selective sweeps, and
    models of the distribution of fitness effects (DFE).
    Further, we describe how these can be applied not only genome-wide but to
    genomic regions with a particular annotation, specific to a given species available
    through the \stdpopsim application programming interface (API), and combined with a parameterized model of
    demography and recombination to provide a realistic simulation of
    genetic variation in a population.
    We then provide a series of examples of how these models can be used
    to benchmark and compare the performance of different methods for
    using genetic data to infer demographic history, the distribution of fitness effects,
    and the targets of recent positive selection.

@@

    As with other aspects of \stdpopsim, we intend the selection models to be as biologically accurate as possible.
    Thus, the \stdpopsim catalog provides \texttt{Annotation} objects based on species' publicly available functional genomic elements
    and \texttt{DFE} objects based on published DFE estimates (Figure \ref{fig:schematic}A).
    By using annotation objects, one can, for example, simulate populations where selected mutations (whose selection
    coefficients are drawn from a specified DFE) occur within annotation regions (e.g. exons), while all mutations
    occurring outside of these regions do not affect fitness.
    There are relatively few species with published DFE estimates in the literature.
    \stdpopsim currently has implemented DFEs for five species in the catalog:
    \textit{Arabidopsis thaliana} \citep{huber2018gene},
    \textit{Drosophila melanogaster} \citep{ragsdale2016triallelic,huber2017determining,zhen2021greater},
    humans \citep{huber2017determining,kim2017inference,kyriazis2023using,castellano2019compmarison,castellano2019compmarison,rodrigues2024shared},
    \textit{Mus musculus} \citep{booker2021selective},
    and the vaquita porpoise \textit{Phocoena sinus} \citep{robinson2022critically}.
    While the DFEs are from a limited number of species, these DFEs can be applied to other species
    if and when it is suitable,
    namely, when a species of interest lacks a pubished DFE in the catalog \revpoint{1}{8}.
    For instance, one could simulate a butterfly species with a gamma-distributed DFE originally
    estimated from humans, or a human population with a DFE estimated from \textit{Drosophila}.
    Indeed, the DFE labeled \texttt{HomSap/Mixed\_K23} is recommended by \citet{kyriazis2023using}
    for ``general'' use across mammals (lacking more specific information).
    Furthermore, the user can specify a custom DFE and provide their own annotations
    of functional elements to simulate selection in a species for which we do not yet have
    a published DFE included in the catalog.

@@

    % sweep interface
    While the \texttt{DFE} class facilitates the simulation of non-neutral
    variation across a sequence, it does not provide a means of specifying the
    origin and fate of particular selected alleles.  Thus, we have also
    implemented an API in \stdpopsim (\texttt{stdpopsim.selective\_sweep}) that
    enables selective sweeps to be simulated with a high degree of control.
    This function augments a demographic model by introducing a mutation at a
    particular time and position along the sequence; sets the selection
    coefficient of the mutation to a positive value over a given time interval;
    and conditions the simulation such that the mutation is above a particular
    frequency at the beginning and end of the sweep period.  The conditioning
    is implemented via rejection sampling; if the advantageous allele is lost
    or does not have a frequency exceeding a user-specified threshold at the
    beginning or end of the sweep, the simulation is restarted from the
    introduction of the advantageous allele.  If there are competing
    advantageous alleles (e.g.  simultaneous sweeps at distinct loci) then the
    simulation is restarted from the introduction of the first of these.  As
    this functionality is implemented on top of the existing \stdpopsim API, it
    may be combined with other models of selection and demography to simulate
    the combined effects of multiple, disparate evolutionary processes on
    genetic variation in a population.

@@

    To expand these observations to additional species and to highlight the ease of comparison enabled by \stdpopsim,
    we performed a similar benchmark using the vaquita porpoise \textit{Phocoena sinus}.
    We simulated 100 genomes under a two-epoch demographic model inferred for vaquita by \textcite{robinson2022critically},
    and a constant recombination rate across the genome (see \textbf{Methods}).
    In simulations with selection, we applied the DFE inferred by \textcite{robinson2022critically} to exons
    annotated from the vaquita genome assembly.
    This DFE implements a relationship between selection and dominance
    in which very deleterious mutations (with selection coefficient $s<-0.1$) are fully recessive
    (dominance coefficient $h=0$) and weakly deleterious mutations ($s\geq -0.001$) are nearly
    additive ($h=0.4$; see \textbf{Methods}).
    As in the human simulations, we see that the presence of selection
    decreases polymorphism in genomes simulated with selection, but that the effect
    is only readily apparent within exonic regions (Figure \ref{fig:vaquita-summary-stats}).
    For these simulations, the SFS-based method (\stairway) produces more accurate
    inference than the two methods based on the sequential Markovian coalescent
    (\smcpp and \msmc; see Figure \ref{fig:vaquita-demography}).
    Regardless of these differences, we see that background selection again does not
    appear to considerably influence the inference of any of the four methods for this species,
    at least for the parameterization used here,
    even though vaquita has a very different evolutionary history than humans.

@@

    The exploration of performance among methods done here is not meant to be thorough
    benchmarking. Rather, we include these analyses as examples to highlight the utility of \stdpopsim
    for both benchmarking and other tasks where researchers would benefit from the ability to perform
    simulations using parts of published population genetic models. in a streamlined and quality-controlled fashion.
    Having said that, there are a number of interesting results that merit discussion.
    The first pertains to estimation of demographic history ($N_e(t)$) in the context of
    linked purifying selection. Our simulations of human and vaquita genomes
    model deleterious mutations only at exonic positions of the genome.
    As shown in Figures \ref{fig:homsap-summary-stats} and \ref{fig:vaquita-summary-stats},
    this combination only produces sizable decreases in polymorphism at exonic positions,
    which represent a small minority of sites within the genome, and does not lead to large-scale
    perturbations in genome-wide diversity. Thus, it is not surprising that estimates of $N_e(t)$
    from genome-wide data from which exons have been masked should be accurate
    (e.g., Figures \ref{fig:human-demography} and \ref{fig:vaquita-demography}).
    Indeed our results echo those of \citet{marsh2024biases} who found \revpoint{AE}{1}
    similar results on realistic human simulations that included selection.
    However, the question remains to what extent this would be true in empirical data where
    selection is not constrained to coding positions. For instance, we know
    that many genomes harbor large numbers
    of conserved non-coding elements \citep[e.g.,][]{siepel2005evolutionarily} with extremely
    strong selection acting on them \citep{katzman2007human,mclean2008dispensability}.
    We thus caution regarding extrapolation from our results. Future studies might build upon
    the annotations we used here to include selection at other portions of the genome as well
    as mixtures of DFEs across sites.

    A second important finding is that inference of the DFE
    is sensitive to the dominance of deleterious mutations.
    All three of the DFE-inference methods applied here assume that deleterious mutations act
    in an additive fashion ($h=0.5$) by default.
    However, the simulated DFE for the vaquita genome included highly recessive mutations.
    Specifically, these simulations used a DFE where mutations with $s<-0.01$ are quite recessive,
    with $h<=0.01$, and where mutations with $-0.01<s<-0.001$ have $h=0.1$.
    We found that the three DFE-inference methods underestimated $E[s]$ and overestimated the shape parameter (Figure \ref{fig:vaquita-dfe}A-B).
    This performance is not surprising since decreasing $h$ for a given distribution of $s$ will lead to a decrease in $hs$,
    or an apparent decrease in the amount of selection.
    Thus, fitting a mis-specified DFE that assumes $h=0.5$ leads to underestimates of $E[s]$. \revpoint{1}{7}
    %IG: added this to respond to comment 1.7.
    %IG: I quote this in the response, so if we edit this, we should copy modified version to the response.
    Our analysis suggests that the distributions of $s$ estimated by these methods
    provide a reasonable approximation for the true distribution of $hs$ (Figure \ref{fig:vaquita-dfe}C).
    This points to a notable limitation of most existing DFE inference methods,
    which assume that selection coefficients are gamma-distributed.
    %DRS: Is the limitatio here that selection coefficients are gamma-distributed, or rather that h is fixed?
    As shown in Figure \ref{fig:vaquita-dfe}C,
    while a gamma distribution might fit the conditional distribution of $s$ given $h$, a relationship between $h$ and $s$ might result in a magrinal distribution for $hs$ which is not well approximated by a gamma distribution.

    %IG: split this into a separate paragraph because this ended up being a bit long
    Overall, these results are consistent with prior work showing that it is challenging to separately
    infer the DFE of $s$ along with $h$ \citep{veeramah2014evidence, kyriazis2024constraining, balick2022overcoming} \revpoint{1}{6}
    and that a large proportion ($>5\%$) of recessive deleterious mutations can confound inferences of $s$ \citep{wade2023quantifying}.
    Given the plethora of evidence for recessive deleterious mutations
    \citep{mukai1972mutation, agrawal2011inferences, huber2018gene, di2024revisiting},
    these results suggest the need for care in DFE inference.
    Kyriazis and Lohmueller \citeyear{kyriazis2024constraining} inferred the DFE of $s$ for nonsynonymous mutations
    in humans when considering different values of $h$.
    Intriguingly, additive models showed a satisfactory fit to the SFS of nonsynonymous variants in humans,
    and more complex models of dominance did not substantially improve the fit.
    Nevertheless, models including recessive deleterious mutations, like those simulated here for the vaquita genome,
    show a similar fit to the SFS and may be more biologically realistic than fully additive models, 
    given the evidence for the presence of recessive deleterious mutations.
    More broadly, new computational approaches are needed to precisely quantify the DFE and the covariance of $h$ and $s$.

@@

    % NSP: added to address reviewer 1's comments asking for more detail. Not adding
    % any detail regarding the lower-level interface (particular "extended events") as
    % these may change.
    \subsection*{Selective sweeps and rejection sampling}

    Selective sweeps are implemented in the \slim engine by introducing a
    mutation with a fitness effect of $h s$ where $h$ is the dominance
    coefficient (as for the DFE model) and $s \geq 0$ is the selection
    coefficient. The allele is introduced in a given population at a specified
    time and genomic position, and may be either globally or locally adaptive
    (so that the fitness effect is confined to the population of origin) over a
    fixed duration. The start of the sweep may be offset from the introduction
    of the allele, to model selection on standing genetic variation (so-called
    ``soft sweeps'').

    Crucially, the advantageous allele must remain extant over the course of
    the sweep; this conditioning is accomplished via rejection sampling,
    whereby the simulation is restarted from the onset of the sweep if the
    allele drifts out of the population of origin. The conditioning may
    optionally be extended to reject trajectories where the frequency at the
    beginning and end of the sweep period is below a specified threshold. If
    there are competing advantageous alleles (simultaneous sweeps at distinct
    loci) and one of these does not satisfy the acceptance conditions, then the
    simulation is restarted from the onset of the first sweep; this avoids
    conditioning on particular (partial) allele frequency trajectories for the
    remaining alleles.  A downside of this strategy is that rejection becomes
    more likely with increasing numbers of simultaneous sweeps or with
    hard-to-satisfy constraints; but it allows for greater flexibility in sweep
    specification and for interoperability with the \stdpopsim DFE model.

>>>>

% add commands for the DFE inference methods
\newcommand{\dfe}{\texttt{dfe-alpha}\xspace}
\newcommand{\polydfe}{\texttt{polyDFE}\xspace}
\newcommand{\dadicli}{\texttt{dadi-cli}\xspace}
\newcommand{\dadi}{\texttt{dadi}\xspace}
\newcommand{\grapes}{\texttt{GRAPES}\xspace}

@@

\section*{Introduction}
    \label{introduction}
    % selection
    Selection is a fundamental force in evolution, shaping the
    genetic diversity of populations and driving the adaptation of
    species to their environments. The effects of selection
    on genetic variation are complex, and can be difficult to disentangle
    from other evolutionary processes such as mutation, recombination,
    and genetic drift \citep[e.g.,][]{ohta1973slightly,lewontin1973distribution, kimura1985neutral, Tajima1989, gillespie1991causes, kern2018neutral}. \revpoint{2}{4}
    For instance, changes in population size can lead to fluctuations
    in genetic diversity across a recombining chromosome
    that can mimic the effects of selection \citep{simonsen1995properties},
    leading to spurious inferences about the strength and targets of genetic adaptation
    \citep{simonsen1995properties,akey2004population,nielsen2005genomic}.
    In turn, selection can confound our ability to infer demographic
    history from allele frequencies \citep{ewing2016consequences,schrider2016effects} and
    estimates of inverse coalescent rate \citep{schrider2016effects, johri2021impact, cousins2024accurate}.
    Thus, it is imperative to jointly account for the effects of selection
    and demography when inferring evolutionary history from genetic data \citep[e.g.,][]{sheehan2016deep,johri2020toward},
    yet the number of tools for doing so remain limited.

@@

    % goals
    Here, we provide an overview of a major new addition
    to \stdpopsim---the inclusion of models of selection.
    We begin by describing the models of selection that we have implemented,
    as well as the parameter choices that are available to the user.
    This includes models of background selection, selective sweeps, and
    models of the distribution of fitness effects (DFE).
    Further, we describe how these can be applied not only genome-wide but to
    genomic regions with a particular annotation, specific to a given species available
    through the \stdpopsim application programming interface (API), and combined with a parameterized model of
    demography and recombination to provide a realistic simulation of
    genetic variation in a population.
    We then provide a series of examples of how these models can be used
    to benchmark and compare the performance of different methods for
    using genetic data to infer demographic history, the distribution of fitness effects,
    and the targets of recent positive selection.
    The examples use genomes of both humans (\textit{Homo sapiens})
    and the critically endangered Vaquita porpoise (\textit{Phocoena sinus}),
    which provides an interesting comparison due to its small recent population size. \revpoint{1}{3}

@@

    As with other aspects of \stdpopsim, we intend the selection models to be as biologically accurate as possible.
    Thus, the \stdpopsim catalog provides \texttt{Annotation} objects based on species' publicly available functional genomic elements
    and \texttt{DFE} objects based on published DFE estimates (Figure \ref{fig:schematic}A).
    By using annotation objects, one can, for example, simulate populations where selected mutations (whose selection
    coefficients are drawn from a specified DFE) occur within annotation regions (e.g. exons), while all mutations
    occurring outside of these regions do not affect fitness.
    There are relatively few species with published DFE estimates in the literature.
    \stdpopsim currently has implemented DFEs for five species in the catalog:
    \textit{Arabidopsis thaliana} \citep{huber2018gene},
    \textit{Drosophila melanogaster} \citep{ragsdale2016triallelic,huber2017determining,zhen2021greater},
    humans \citep{huber2017determining,kim2017inference,kyriazis2023using,castellano2019compmarison,castellano2019compmarison,rodrigues2024shared},
    \textit{Mus musculus} \citep{booker2021selective},
    and the vaquita porpoise \textit{Phocoena sinus} \citep{robinson2022critically}.
    While the DFEs are from a limited number of species, these DFEs can be applied to other species
    if and when it is suitable,
    namely, when a species of interest lacks a published DFE in the catalog \revpoint{1}{8}.
    For instance, one could simulate a butterfly species with a gamma-distributed DFE originally
    estimated from humans, or a human population with a DFE estimated from \textit{Drosophila}.
    Indeed, the DFE labeled \texttt{HomSap/Mixed\_K23} is recommended by \citet{kyriazis2023using}
    for ``general'' use across mammals (lacking more specific information).
    Furthermore, the user can specify a custom DFE and provide their own annotations
    of functional elements to simulate selection in a species for which we do not yet have
    a published DFE included in the catalog.

@@

    % sweep interface
    While the \texttt{DFE} class facilitates the simulation of non-neutral
    variation across a sequence, it does not provide a means of specifying the
    origin and fate of particular selected alleles.  Thus, we have also
    implemented an API in \stdpopsim (\texttt{stdpopsim.selective\_sweep}) that
    enables selective sweeps to be simulated with a high degree of control.
    This function augments a demographic model by introducing a mutation at a
    particular time and position along the sequence; sets the selection
    coefficient of the mutation to a positive value over a given time interval;
    and conditions the simulation such that the mutation is above a particular
    frequency at the beginning and end of the sweep period.  The conditioning \llabel{sweep_conditioning}
    is implemented via rejection sampling; if the advantageous allele is lost
    or does not have a frequency exceeding a user-specified threshold at the
    beginning or end of the sweep, the simulation is restarted from the
    introduction of the advantageous allele.  If there are competing
    advantageous alleles (e.g.  simultaneous sweeps at distinct loci) then the
    simulation is restarted from the introduction of the first of these.  As
    this functionality is implemented on top of the existing \stdpopsim API, it
    may be combined with other models of selection and demography to simulate
    the combined effects of multiple, disparate evolutionary processes on
    genetic variation in a population.

@@

    To expand these observations to additional species and to highlight the ease of comparison enabled by \stdpopsim,
    we performed a similar benchmark using the vaquita porpoise \textit{Phocoena sinus}.
    We simulated 100 genomes under a two-epoch demographic model inferred for vaquita by \textcite{robinson2022critically},
    and a constant recombination rate across the genome (see \textbf{Methods}).
    This is particularly interesting because the model was inferred assuming neutrality (with \dadi)
    and used to inform conservation efforts for this critically endangered species. \llabel{vaquita_note}
    In simulations with selection, we applied the DFE inferred by \textcite{robinson2022critically} to exons
    annotated from the vaquita genome assembly.
    This DFE implements a relationship between selection and dominance
    in which very deleterious mutations (with selection coefficient $s<-0.1$) are fully recessive
    (dominance coefficient $h=0$) and weakly deleterious mutations ($s\geq -0.001$) are nearly
    additive ($h=0.4$; see \textbf{Methods}).
    As in the human simulations, we see that the presence of selection
    decreases polymorphism in genomes simulated with selection, but that the effect
    is only readily apparent within exonic regions (Figure \ref{fig:vaquita-summary-stats}).
    For these simulations, the SFS-based method (\stairway) produces more accurate
    inference than the two methods based on the sequential Markovian coalescent
    (\smcpp and \msmc; see Figure \ref{fig:vaquita-demography}).
    Regardless of these differences, we see that background selection again does not
    appear to considerably influence the inference of any of the four methods for this species,
    at least for the parameterization used here,
    even though vaquita has a very different evolutionary history than humans.

@@

    The exploration of performance among methods done here is not meant to be thorough
    benchmarking.
    Rather, we include these analyses as examples to highlight the utility of \stdpopsim \llabel{not_the_point}
    for both benchmarking and other tasks where researchers would benefit from the ability to perform
    simulations using parts of published population genetic models in a streamlined and quality-controlled fashion.
    Having said that, there are a number of interesting results that merit discussion.
    The first pertains to estimation of demographic history ($N_e(t)$) in the context of
    linked purifying selection. Our simulations of human and vaquita genomes
    model deleterious mutations only at exonic positions of the genome.
    As shown in Figures \ref{fig:homsap-summary-stats} and \ref{fig:vaquita-summary-stats},
    this combination only produces sizable decreases in polymorphism at exonic positions,
    which represent a small minority of sites within the genome, and does not lead to large-scale
    perturbations in genome-wide diversity. Thus, it is not surprising that estimates of $N_e(t)$
    from genome-wide data from which exons have been masked should be accurate
    (e.g., Figures \ref{fig:human-demography} and \ref{fig:vaquita-demography}).
    Indeed our results echo those of \citet{marsh2024biases} who found \revpoint{AE}{1}
    similar results on realistic human simulations that included selection.
    However, the question remains to what extent this would be true in empirical data where
    selection is not constrained to coding positions. For instance, we know
    that many genomes harbor large numbers
    of conserved non-coding elements \citep[e.g.,][]{siepel2005evolutionarily} with extremely
    strong selection acting on them \citep{katzman2007human,mclean2008dispensability}.
    We thus caution regarding extrapolation from our results. Future studies might build upon
    the annotations we used here to include selection at other portions of the genome as well
    as mixtures of DFEs across sites.

    A second important finding is that inference of the DFE
    is sensitive to the dominance of deleterious mutations.
    All three of the DFE-inference methods applied here assume that deleterious mutations act
    in an additive fashion ($h=0.5$) by default.
    However, the simulated DFE for the vaquita genome included highly recessive mutations.
    Specifically, these simulations used a DFE where mutations with $s<-0.01$ are quite recessive,
    with $h<=0.01$, and where mutations with $-0.01<s<-0.001$ have $h=0.1$.
    We found that the three DFE-inference methods underestimated $E[s]$ and overestimated the shape parameter (Figure \ref{fig:vaquita-dfe}A-B).
    This performance is not surprising since decreasing $h$ for a given distribution of $s$ will lead to a decrease in $hs$,
    or an apparent decrease in the amount of selection.
    Thus, fitting a mis-specified DFE that assumes $h=0.5$ leads to underestimates of $E[s]$. \revpoint{1}{7}
    Our analysis suggests that the distributions of $s$ estimated by these methods
    provide a reasonable approximation for the true distribution of $hs$ (Figure \ref{fig:vaquita-dfe}C).
    This points to a notable limitation of most existing DFE inference methods,
    which assume that selection coefficients are gamma-distributed.
    %DRS: Is the limitatio here that selection coefficients are gamma-distributed, or rather that h is fixed?
    As shown in Figure \ref{fig:vaquita-dfe}C,
    while a gamma distribution might fit the conditional distribution of $s$ given $h$, a relationship between $h$ and $s$ might result in a marginal distribution for $hs$ which is not well approximated by a gamma distribution.

    %IG: split this into a separate paragraph because this ended up being a bit long
    Overall, these results are consistent with prior work showing that it is challenging to separately
    infer the DFE of $s$ along with $h$ (\textcite{wright1937distribution, veeramah2014evidence, simons2014deleterious, fuller2019measuring, balick2022overcoming, kyriazis2024constraining}; reviewed in \textcite{fuller2019measuring}) \revpoint{1}{6}
    and that a large proportion ($>5\%$) of recessive deleterious mutations can confound inferences of $s$ \citep{wade2023quantifying}.
    Given the plethora of evidence for recessive deleterious mutations
    \citep{mukai1972mutation, agrawal2011inferences, huber2018gene, di2024revisiting},
    these results suggest the need for care in DFE inference.
    Kyriazis and Lohmueller \citeyear{kyriazis2024constraining} inferred the DFE of $s$ for nonsynonymous mutations
    in humans when considering different values of $h$.
    Intriguingly, additive models showed a satisfactory fit to the SFS of nonsynonymous variants in humans,
    and more complex models of dominance did not substantially improve the fit.
    Nevertheless, models including recessive deleterious mutations, like those simulated here for the vaquita genome,
    show a similar fit to the SFS and may be more biologically realistic than fully additive models, 
    given the evidence for the presence of recessive deleterious mutations.
    More broadly, new computational approaches are needed to precisely quantify the DFE and the covariance of $h$ and $s$.

@@

    \subsection*{Selective sweeps and rejection sampling}

    % NSP: added to address reviewer 1's comments asking for more detail. Not adding
    % any detail regarding the lower-level interface (particular "extended events") as
    % these may change.
    %
    %% For reference, from the docs on selective_sweep():
    % Creates a list of extended events corresponding to a selective sweep at a
    % single site (see :meth:`Contig.add_single_site`) that may subsequently be
    % passed to the simulation engine. The sequence of events is:

    %     (1) In generation `mutation_generation_ago`, a **neutral** mutation is
    %         introduced into `population`.

    %     (2) In generation `start_generation_ago`, the mutation becomes
    %         beneficial (whether globally or locally is controlled by the
    %         `globally_adaptive` option). If the frequency of the mutation in
    %         `population` is below `min_freq_at_start` in this generation, the
    %         simulation will restart from `mutation_generation_ago`.

    %     (3) In the generation after `end_generation_ago`, the mutation reverts to
    %         neutrality in `population`. If the frequency of the mutation in
    %         `population` is below `min_freq_at_end` in this generation, the
    %         simulation will restart from `mutation_generation_ago`.

    % During the sweep, the fitnesses of individuals that are homozygous or
    % heterozygous for the beneficial mutation are `1 + selection_coeff` and  `1
    % + selection_coeff * dominance_coeff`, respectively. If `globally_adaptive`
    % is `True` (the default), then all individuals carrying the mutation are
    % impacted regardless of the population they belong to. Otherwise, the
    % mutation only influences fitness within `population`.

    % If the mutation is lost in `population` at any point between
    % `mutation_generation_ago` and `end_generation_ago`, then the simulation
    % will restart from `mutation_generation_ago`. The effect of "restarting"
    % (aka "rejection sampling") is that the resulting simulations are
    % conditioned on the mutation being extant after time
    % `mutation_generation_ago` with frequency above `min_freq_at_start` at
    % `start_generation_ago` and `min_freq_at_end` at `end_generation_ago`.

    % Because the simulation will restart until the allele frequency conditions
    % are satisfied, care must be taken to ensure that these are reasonable. For
    % example, if `start_generation_ago` is very close to
    % `mutation_generation_ago` and `min_freq_at_start` is substantially greater
    % than zero, the vast majority of proposed allele frequency trajectories will
    % be rejected and the simulation may take an infeasibly long time to
    % complete.

    Selective sweeps are implemented in the \slim engine by introducing a
    mutation with a fitness effect of $h s$ in heterozygotes and $s$ in homozygotes,
    where $h$ is the dominance coefficient (as for the DFE model) and $s \geq 0$ is the selection
    coefficient. The allele is introduced in a given population at a specified
    time and genomic position, and may be either globally or locally adaptive
    (so that the fitness effect is confined to the population of origin) over a
    fixed duration. The start of the sweep may be offset from the introduction
    of the allele, to model selection on standing genetic variation (so-called
    ``soft sweeps'').
